Perturbing SU($n$)-symmetric interactions

### 2020-03-17 collective_sun/sun_perturbation.tex
re-wrote (and corrected) the section on using symmetries to reduce the multi-body eigenvalue problem

@@

The first-order effective Hamiltonian $H_2^{(1)}$ induced on the
permutationally symmetric manifold $\M_0$ by the two-body perturbation
$\V_2$ in \eqref{eq:perturbations} is simply the restriction of $\V_2$
onto $\M_0$:
\begin{align}
  H_2^{(1)} = \sum_O \sum_{p<q} w_{Opq} \P_0 O_{pq} \P_0
  \EQPS \sum_O \sum_{p<q} w_{Opq} O_{1,2}
  \EQPS \sum_O \bar w_O \col{O},
\end{align}
where
\begin{align}
  \bar w_O \equiv {N \choose 2}^{-1} \sum_{p<q} w_{Opq},
  &&
  \col{O} \equiv \sum_{p<q} O_{pq},
\end{align}
are an average of $w_{Opq}$ and a collective version of the two-spin
operator $O_{pq}$.  If the two-spin operator
$O=X\otimes Y+Y\otimes X$, then
\begin{align}
  H_2^{(1)} \EQPS \f12 \sum_{\p{X,Y}} \bar w_{\p{X,Y}}
  \p{\col{X}\,\col{Y} + \col{Y}\,\col{X} - \col{XY} - \col{YX}}.
\end{align}
In order to compute the second-order effective Hamiltonian
$H_2^{(2)}$, as before we pick an arbitrary permutationally symmetric
state $\ket\psi\in\M_0$ and expand (see Section \ref{sec:eigenstates})
\begin{align}
  H_0 \V_2 \ket\psi
  = E_0 \V_2 \ket\psi
  + \sum_O \sum_{p<q}
  \sp{\sum_k \p{h_{pk} w_{Okq} + h_{qk} w_{Opk}}
    - \tilde h_{pq} w_{Opq}}
  O_{pq} \ket\psi,
  \label{eq:H_V2_psi}
\end{align}
where to keep notation compact, we define
\begin{align}
  \tilde h_{pq} \equiv h_p + h_q - 2 h_{pq},
  &&
  h_p \equiv \sum_q h_{pq},
\end{align}
and we define $w_{Opq}$ for all $p,q$ (as opposed to only $p<q$) by
enforcing $w_{Opq}=w_{Oqp}$ and $w_{Opp}=0$.  We thus find that the
vector $\V_2^\Delta\ket\psi$ (indexed by $\Delta$) is an eigenvector
of the interaction Hamiltonian $H_0$ if its coefficients
$\v{\m w}_O^\Delta$ all satisfy the eigenvalue equation
\begin{align}
  \check{\m h}_2 \c \v{\m w} = \Delta \v{\m w},
  \label{eq:V2_eig}
\end{align}
where
\begin{align}
  \check{\m h}_2
  \equiv \sum_{p<q} \ket{\set{p,q}} \sp{\sum_{k\notin\set{p,q}}
    \p{h_{pk} \bra{\set{k,q}} + h_{qk} \bra{\set{p,k}}}
    - \tilde h_{pq} \bra{\set{p,q}}}.
  \label{eq:V2_eig_mat}
\end{align}
We explicitly exclude $k\in\set{p,q}$ in \eqref{eq:V2_eig_mat} because
these terms vanish in \eqref{eq:H_V2_psi} from the fact that
$h_{kk}=w_{Okk}=0$.  Solving the general eigenvalue problem in
\eqref{eq:V2_eig} requires diagonalizing the
${N \choose 2}\times{N \choose 2}\sim N^2\times N^2$ matrix
$\check{\m h}_2$.  When the interaction Hamiltonian $H_0$ and
perturbation $\V_M$ are translationally invariant, however, this
eigenvalue problem can be reduced to that of diagonalizing a matrix of
dimensions $\sim N\times N$; we perform this reduction in Section
\ref{sec:trans_inv}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Constructing multi-body excitation energy eigenstates}
\label{sec:eigenstates}

In this section, we simplify the products of the form
$H_0\V_M\ket\psi$ to arrive at expansions such as \eqref{eq:H_V1_psi}
and \eqref{eq:H_V2_psi}, which define conditions under which a
multi-body perturbation $\V_M$ generates eigenstates of the
SU($n$)-symmetric interaction Hamiltonian $H_0$ in \eqref{eq:H_0} when
acting on a permutationally symmetric state $\ket\psi\in\M_0$.  Here
$\V_M$ is an $M$-body perturbation of the form
\begin{align}
  \V_M \equiv \sum_{k\in\C_N\p{M}} w_k O_k.
\end{align}
where $O$ is an $M$-spin operator that is invariant under arbitrary
permutation of its tensor factors; $k\equiv\p{k_1,k_2,\cdots,k_M}$ is
a choice of $M$ distinct spins that $O$ acts on; and $\C_N\p{n}$ is
the set of all distinct choices of $n$ elements from a set of size
$N$.

@@

When the interaction Hamiltonian $H_0$ is translationally invariant,
the single-body eigenvalue problem in \eqref{eq:H_V1_psi_eig} is
exactly solvable.  In this case, the couplings $h_{pq}$ depend only on
the separation $\abs{p-q}$, so the eigenvectors of $\m h$ are plane
waves of the form
\begin{align}
  \v v_k \equiv \sum_p e^{ip\c k} \ket{p},
\end{align}
where on a $D$-dimensional periodic lattice of $N=L^D$ spins, lattice
sites are indexed by vectors
$p\in\ZZ_L^D\simeq\set{0,1,\cdots,L-1}^{\otimes D}$, and wavenumbers
take on values $k\in\ZZ_L^D\times2\pi/L$.  The corresponding
eigenvalues of $\m h$ can be determined by expanding
\begin{align}
  \m h\c\v v_k = \sum_{p,q} h_{pq} e^{iq\c k} \ket{p}
  = \sum_{p,d} h_{p,p+d} e^{i\p{p+d}\c k} \ket{p}
  = \sum_d h_{0,d} e^{id\c k} \v v_k
  = \sum_d h_{0,d} \cos\p{d\c k} \v v_k,
\end{align}
where the imaginary terms vanish because $h_{0,d}=h_{0,-d}$.  The
remainder of \eqref{eq:H_V1_psi_eig} that we need to sort out is
$\diag\v h$, where all $h_p=\sum_qh_{pq}=\sum_dh_{0,d}$ are equal,
which implies that $\diag\v h=\sum_dh_{0,d}$ is a scalar.  We thus
find that,
\begin{align}
  \p{\m h - \diag\v h}\c\v v_k = \Delta_k \v v_k,
  &&
  \Delta_k \equiv \sum_d h_{0,d} \sp{\cos\p{d\c k}-1}.
\end{align}

@@

  \sum_{a=1}^M h_{p k_a} w_k \Pi_{p k_a} O_k \ket\psi.

@@

$k_{ap}\equiv\p{k_1,k_2,\cdots,k_{a-1},p,k_{a+1},\cdots,k_M}$, i.e.~an
element of $\C_N\p{M}$ in which the $a$-th number $k_a$ has been
replaced by $p$, we can simplify

@@

  = O_{k_{ap}}\ket\psi,

@@

  \sum_{a=1}^M h_{pk_a} w_{k_{ap}} O_k \ket\psi.

@@

  \m h\circ\m w \equiv \sum_{a=1}^M \m h\c_a\m w,

@@

  \equiv \sum_{\substack{p\in\ZZ_N\\p\notin k}} \sum_{a=1}^M
  h_{pk_a} w_{k_{ap}}

@@

  \m h\circ\m w - \tilde{\m h} * \m w = \Delta \m w.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Translational invariance}
\label{sec:trans_inv}

Solving the eigenvalue problem in \eqref{eq:H_VM_psi_eig} to find
$M$-body perturbations $\V_M$ that generate states of definite
interaction energy nominally requires diagonalizing a matrix with
dimensions ${N\choose M}\times{N\choose M}\sim N^M\times N^M$.  Here,
we simplify this problem to that of diagonalizing a matrix with
dimensions
$\sim{N-1\choose M-1}\times{N-1\choose M-1}\sim N^{M-1}\times N^{M-1}$
when both the interaction Hamiltonian $H_0$ and the perturbation
$\V_M$ are translationally invariant.  This simplification reduces the
computational cost of solving the $M$-body eigenvalue problem by a
factor of $\O\p{N^3}$.

Our task is essentially to express the multi-body eigenvalue problem
in \eqref{eq:H_VM_psi_eig} in a basis that obeys both permutational
symmetry and translational invariance.  To this end, we first expand
the coupling tensor $\m w$ in a complete basis for symmetric tensors:
\begin{align}
  \m w = \sum_{k\in\C_N\p{M}} w_k \m m_k,
  &&
  \m m_k \equiv \sum_{\sigma\in P_M} \m e_{\sigma\p{k}},
  \label{eq:sym_tensor}
\end{align}
where $P_M$ is the set of all permutations of $M$ symbols, and
$\m e_\ell$ is a unit tensor with one in the entry indexed by $\ell$
and zeros everywhere else.  On a $D$-dimensional lattice of linear
size $L$, translational invariance implies that the coefficients $w_k$
remain the same if all spins indexed by $k$ are shifted by the same
displacement $d\in\ZZ_L^D$.  To account for this invariance, we denote
a translation of all spins in $k$ by a displacement $d\in\ZZ_L^D$ by
$k_d$, and define the translation-symmetrized basis tensors
\begin{align}
  \m m_k^{\t{TS}}
  \equiv \f1{\N_k^{\t{TS}}} \sum_{d\in\ZZ_L^D} \m m_{k_d}
  = \f1{\N_k^{\t{TS}}} \sum_{d\in\ZZ_L^D} \sum_{\sigma\in P_M}
  \m e_{\sigma(k_d)},
\end{align}
where the normalization factor $\N_k^{\t{TS}}$ enforces that the
entries of $\m m_k^{\t{TS}}$ are all either zero or one, which
otherwise might not occur if some translations of $k$ results in the
same choice of spins.  We then define the set $\T_{LD}\p{M}$ of
equivalence classes in $\C_N\p{M}$ under arbitrary translations on
$D$-dimensional lattice of linear size $L$, and expand
\begin{align}
  \m w = \sum_{k\in\T_{LD}\p{M}} w_k \m m_k^{\t{TS}}.
  \label{eq:sym_shift_tensor}
\end{align}
Having expanded $\m w$ in a basis that respects permutational symmetry
and translational invariance, we need to express the eigenvalue
equation \eqref{eq:H_VM_psi_eig} in the same basis.  We therefore
expand
\begin{align}
  \m h\circ\m w
  = \sum_{k\in\T_{LD}\p{M}} \sum_{p\in\ZZ_L^D} \sum_{a=1}^M
  h_{pk_a} w_{k_{ap}} \m m_k^{\t{TS}},
  &&
  \tilde{\m h} * \m w = \sum_{k\in\T_{LD}\p{M}}
  \tilde h_k w_k \m m_k^{\t{TS}},
\end{align}
which allows us to write the generalized eigenvalue problem in
\eqref{eq:H_VM_psi_eig} as
\begin{align}
  \check{\m h}\c\v{\m w} = \Delta\v{\m w},
\end{align}
where
\begin{align}
  \check{\m h}
  \equiv \sum_{k\in\T_{LD}\p{M}} \sum_{p\in\ZZ_L^D} \sum_{a=1}^M
  h_{pk_a} \op{k}{k_{ap}}
  - \sum_{k\in\T_{LD}\p{M}} \tilde h_k \op{k},
  &&
  \v{\m w} \equiv \sum_{k\in\T_{LD}\p{M}} w_k \ket{k}.
\end{align}
In order to make sense of $\check{\m h}$ as written above, for each
$k\in\T_{LD}\p{M}$ we enforce a canonical choice of spins
$\tilde k\in k\subset\C_N\p{M}$; we define $k_{ap}$ to be the
equivalence class of $\tilde k_{ap}$ (where $\tilde k_{ap}$ is equal
to $\tilde k$ with the $a$-th spin $k_a$ replaced by $p$); and we
define $\ket{k}=0$ if $\tilde k$ has any repeated values.  The matrix
$\check{\m h}$ has dimensions
$\abs{\T_{LD}\p{M}}\times\abs{\T_{LD}\p{M}}$, where
$\abs{\T_{LD}\p{M}} \approx { N-1 \choose M-1 }/M \sim N^{M-1}$.

>>>>

% alphanumeric footnotes
\renewcommand*{\thefootnote}{\alph{footnote}}

@@

The first-order effective Hamiltonian $H_2^{(1)}$ induced on the
permutationally symmetric manifold $\M_0$ by the two-body perturbation
$\V_2$ in \eqref{eq:perturbations} is simply the restriction of $\V_2$
onto $\M_0$:
\begin{align}
  H_2^{(1)} = \sum_O \sum_{p<q} w_{Opq} \P_0 O_{pq} \P_0
  \EQPS \sum_O \sum_{p<q} w_{Opq} O_{1,2}
  \EQPS \sum_O \bar w_O \col{O},
\end{align}
where
\begin{align}
  \bar w_O \equiv {N \choose 2}^{-1} \sum_{p<q} w_{Opq},
  &&
  \col{O} \equiv \sum_{p<q} O_{pq},
\end{align}
are an average of $w_{Opq}$ and a collective version of the two-spin
operator $O_{pq}$.  If the two-spin operator
$O=X\otimes Y+Y\otimes X$, then
\begin{align}
  H_2^{(1)} \EQPS \f12 \sum_{\p{X,Y}} \bar w_{\p{X,Y}}
  \p{\col{X}\,\col{Y} + \col{Y}\,\col{X} - \col{XY} - \col{YX}}.
\end{align}
In order to compute the second-order effective Hamiltonian
$H_2^{(2)}$, as before we pick an arbitrary permutationally symmetric
state $\ket\psi\in\M_0$ and expand (see Section \ref{sec:eigenstates})
\begin{align}
  H_0 \V_2 \ket\psi
  = E_0 \V_2 \ket\psi
  + \sum_O \sum_{p<q}
  \sp{\sum_k \p{h_{pk} w_{Okq} + h_{qk} w_{Opk}}
    - \tilde h_{pq} w_{Opq}}
  O_{pq} \ket\psi,
  \label{eq:H_V2_psi}
\end{align}
where to keep notation compact, we define
\begin{align}
  \tilde h_{pq} \equiv h_p + h_q - 2 h_{pq},
  &&
  h_p \equiv \sum_q h_{pq},
\end{align}
and we define $w_{Opq}$ for all $p,q$ (as opposed to only $p<q$) by
enforcing $w_{Opq}=w_{Oqp}$ and $w_{Opp}=0$.  We thus find that the
vector $\V_2^\Delta\ket\psi$ (indexed by $\Delta$) is an eigenvector
of the interaction Hamiltonian $H_0$ if its coefficients
$\v{\m w}_O^\Delta$ all satisfy the eigenvalue equation
\begin{align}
  \check{\m h}_2 \c \v{\m w} = \Delta \v{\m w},
  \label{eq:V2_eig}
\end{align}
where
\begin{align}
  \check{\m h}_2
  \equiv \sum_{p<q} \ket{\set{p,q}} \sp{\sum_{k\notin\set{p,q}}
    \p{h_{pk} \bra{\set{k,q}} + h_{qk} \bra{\set{p,k}}}
    - \tilde h_{pq} \bra{\set{p,q}}},
  &&
  \v{\m w} \equiv \sum_{p<q} w_{pq} \ket{\set{p,q}}.
  \label{eq:V2_eig_mat}
\end{align}
We explicitly exclude $k\in\set{p,q}$ in \eqref{eq:V2_eig_mat} because
these terms vanish in \eqref{eq:H_V2_psi} from the fact that
$h_{kk}=w_{Okk}=0$.  Solving the general eigenvalue problem in
\eqref{eq:V2_eig} nominally requires diagonalizing the
${N \choose 2}\times{N \choose 2}\sim N^2\times N^2$ matrix
$\check{\m h}_2$.  When the interaction Hamiltonian $H_0$ and
perturbation $\V_M$ are translationally invariant, however, this
eigenvalue problem can be reduced to that of diagonalizing a matrix of
dimensions $\sim N\times N$, and isotropy can reduce this problem even
further.  We discuss these reductions in Section
\ref{sec:multi_body_symmetries}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Constructing excitation energy eigenstates}
\label{sec:eigenstates}

In this section, we simplify the products of the form
$H_0\V_M\ket\psi$ to arrive at expansions such as \eqref{eq:H_V1_psi}
and \eqref{eq:H_V2_psi}, which define conditions under which a
multi-body perturbation $\V_M$ generates eigenstates of the
SU($n$)-symmetric interaction Hamiltonian $H_0$ in \eqref{eq:H_0} when
acting on a permutationally symmetric state $\ket\psi\in\M_0$.  Here
$\V_M$ is an $M$-body perturbation of the form
\begin{align}
  \V_M \equiv \sum_{k\in\C_N\p{M}} w_k O_k.
\end{align}
where $O$ is an $M$-spin operator that is invariant under arbitrary
permutation of its tensor factors; $k\equiv\p{k_1,k_2,\cdots,k_M}$ is
a choice of $M$ distinct spins that $O$ acts on; and $\C_N\p{M}$ is
the set of all distinct choices of $M$ elements from a set of size
$N$.

@@

When the interaction Hamiltonian $H_0$ is translationally invariant,
the single-body eigenvalue problem in \eqref{eq:H_V1_psi_eig} is
exactly solvable.  In this case, the couplings $h_{pq}$ depend only on
the separation $\abs{p-q}$, so the eigenvectors of $\m h$ are plane
waves of the form
\begin{align}
  \v v_k \equiv \sum_p e^{ip\c k} \ket{p},
\end{align}
where on a $D$-dimensional periodic lattice of $N=L^D$ spins, lattice
sites are indexed by vectors
$p\in\ZZ_L^D\simeq\set{0,1,\cdots,L-1}^{\otimes D}$, and wavenumbers
take on values $k\in\ZZ_L^D\times2\pi/L$.  The corresponding
eigenvalues of $\m h$ can be determined by expanding
\begin{align}
  \m h\c\v v_k = \sum_{p,q} h_{pq} e^{iq\c k} \ket{p}
  = \sum_{p,d} h_{p,p+d} e^{i\p{p+d}\c k} \ket{p}
  = \sum_d h_{0,d} e^{id\c k} \v v_k
  = \sum_d h_{0,d} \cos\p{d\c k} \v v_k,
\end{align}
where the imaginary terms vanish because $h_{0,d}=h_{0,-d}$.  The
remainder of \eqref{eq:H_V1_psi_eig} that we need to sort out is
$\diag\v h$, where all $h_p=\sum_qh_{pq}=\sum_dh_{0,d}$ are equal,
which implies that $\diag\v h=\sum_dh_{0,d}$ is a scalar.  We thus
find that
\begin{align}
  \p{\m h - \diag\v h}\c\v v_k = \Delta_k \v v_k,
  &&
  \Delta_k \equiv \sum_d h_{0,d} \sp{\cos\p{d\c k}-1}.
\end{align}

@@

  \sum_{a\in\ZZ_M} h_{p k_a} w_k \Pi_{p k_a} O_k \ket\psi.

@@

$k_{a:p}\equiv\p{k_1,k_2,\cdots,k_{a-1},p,k_{a+1},\cdots,k_M}$,
i.e.~$k$ with the $a$-th number $k_a$ replaced by $p$, we can simplify

@@

  = O_{k_{a:p}}\ket\psi,

@@

  \sum_{a\in\ZZ_M} h_{pk_a} w_{k_{a:p}} O_k \ket\psi.

@@

  \m h\circ\m w \equiv \sum_{a\in\ZZ_M} \m h\c_a\m w,

@@

  \equiv \sum_{\substack{p\in\ZZ_N\\p\notin k}} \sum_{a\in\ZZ_M}
  h_{pk_a} w_{k_{a:p}}

@@

  \m h\circ\m w - \tilde{\m h} * \m w = \Delta \m w,
which can be written in the form
  \check{\m h} \c \v{\m w} = \Delta \v{\m w},

@@

where
  \check{\m h} \equiv \sum_{k\in\C_N\p{M}}
  \sum_{\substack{p\in\ZZ_N\\p\notin k}} \sum_{a\in\ZZ_M}
  h_{pk_a} \op{k}{k_{a:p}}
  - \sum_{k\in\C_N\p{M}} \tilde h_k \op{k},
  \v{\m w} \equiv \sum_{k\in\C_N\p{M}} w_k \ket{k}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Translational invariance, isotropy, and other symmetries}
\label{sec:multi_body_symmetries}

Solving the eigenvalue problem in \eqref{eq:H_VM_psi_eig} to find
$M$-body perturbations $\V_M$ that generate states of definite
interaction energy nominally requires diagonalizing the matrix
$\check{\m h}$ with dimensions
${N\choose M}\times{N\choose M}\sim N^M\times N^M$.  If the
interaction Hamiltonian $H_0$ and multi-body perturbation $\V_M$ have
any symmetries, such as translational invariance isotropy, then we can
use these symmetry to reduce the eigenvalue problem in
\eqref{eq:H_VM_psi_eig}.  Translational invariance, for example, can
reduce this problem to diagonalizing a matrix with dimensions
$\sim{N-1\choose M-1}\times{N-1\choose M-1}\sim N^{M-1}\times
N^{M-1}$, and isotropy can further reduce the problem size by factors
that depend on the lattice geometry.  The complexity of diagonalizing
a matrix with dimensions $d\times d$ is $\O\p{d^3}$, so even a
reduction of $d$ by a factor of 2 yields practically significant gains
(a factor of $2^3=8$) in the runtime of diagonalization.  Here, we
provide a general prescription for exploiting the symmetries of $H_0$
and $\V_M$ to simplify the eigenvalue problem in
\eqref{eq:H_VM_psi_eig}.

Symmetries of $H_0$ and $\V_M$ essentially break the set of choices
$\C_N\p{M}$ into equivalence classes $\S\p{M}$\footnote{For brevity,
  we will suppress the explicit dependence of $\S\p{M}$ on $N$, as
  well as the dependence of $\S\p{M}$ on any other factors such as
  lattice geometry.}, where elements $s\in\S\p{M}$ are subsets
$s\subset\C_N\p{M}$ that are invariant under the appropriate symmetry
group action.  In the case of a translationally invariant and
isotropic system with two-body perturbations, for example, each
equivalence class $s\in\S_2$ would consist of all pairs
$\p{p,q}\in\C_N\p{2}$ that are a fixed distance $\abs{p-q}=d_s$ apart,
i.e.~$s=\set{\p{p,q}\in\C_N\p{2}:\abs{p-q}=d_s}$.

Our task is essentially to express the multi-body eigenvalue problem
in \eqref{eq:H_VM_psi_eig} in a basis that obeys the symmetries under
consideration.  To this end, for any equivalence class $s\in\S\p{M}$
we define a uniform superposition $\ket{s}$ over all choices $k\in s$,
as well as the projector $\P_\S$ onto the space of uniform
superpositions:
\begin{align}
  \ket{s} \equiv \f1{\sqrt{\abs{s}}} \sum_{k\in s} \ket{k},
  &&
  \P_{\S_M} \equiv \sum_{s\in\S\p{M}} \op{s},
\end{align}
where $\abs{s}$ is the number of elements in $s$.  We then expand the
coefficient vector $\v{\m w}$ in this symmetrized basis:
\begin{align}
  \v{\m w} = \sum_{k\in\C_N\p{M}} w_k \ket{k}
  = \sum_{s\in\S_M} w_s \sqrt{\abs{s}} \ket{s},
\end{align}
where $w_s\equiv w_k$ for any $k\in s$.  Finally, we define the
projection of $\check{\m h}$ onto the symmetric subspace:
\begin{align}
  \check{\m h}_{\S_M}
  \equiv \P_{\S_M} \check{\m h} \P_{\S_M}
  = \sum_{r,s\in\S_M} h_{rs} \op{r}{s},
\end{align}
where
\begin{align}
  h_{rs} \equiv \sum_{k,\ell\in\C_N} h_{k\ell} \bk{r|k} \bk{\ell|s}
  = \f1{\sqrt{\abs{r}\abs{s}}}
  \sum_{\substack{k\in r\\\ell\in s}} h_{k\ell}.
\end{align}
In practice, it can be computationally cheaper to construct
\begin{align}
  \check{\m h}_{\S_M} = \sum_{s\in\S_M} \ket{s} \f1{\sqrt{\abs{s}}}
  \sum_{k\in s} \sum_{\substack{p\in\ZZ_N\\p\notin k}} \sum_{a\in\ZZ_M}
  \f{h_{p k_a}}{\sqrt{\abs{\sp{k_{a:p}}}}} \bra{\sp{k_{a:p}}},
\end{align}
where $k_a$ is the $a$-th element of $k$;
$k_{a:p}\equiv\p{k_1,k_2,\cdots,k_{a-1},p,k_{a+1},\cdots,k_M}$ is $k$,
but with the $a$-th number $k_a$ replaced by $p$; and $\sp{k_{a:p}}$
is the equivalence class of $k_{a:p}$.  The reduced multi-body
eigenvalue problem is then
\begin{align}
  \check{\m h}_{\S_M} \c \v{\m w} = \Delta \v{\m w}.
\end{align}
